---
title: "Eating Out"
author: "Trevor Ragazzo"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

This graph is showing that the white race has a over 1000 frequency and the black race was below 200. Overall this graph shows the white race eats out the most and the black and other races eat out about the same. The black and other races had a percentage of 70% of people eating out, while the white race was more than 80% of people eat out. 


```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```

In total we see the white race eating out the most with a little above 80% and less than 17% that does not eat out. The Black race seems to eat out the least between these three groups with 69% eating out and about 31% not eating out. Lastly we see the other races in between the white and black races with 72% eating out and about 27% that does not eat out. 



